--- 
title: "Reproducible Templates _(Book in Development)_"
author: "Melinda K. Higgins"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [manual.bib, packages.bib]
biblio-style: apalike
link-citations: yes
lot: true
lof: true
description: "This book is in development."
---

```{r pkgs1, include=FALSE}
# set up knitr chunk options

# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(message = FALSE)

# set up packages needed
library(bookdown)
library(rmarkdown)
library(knitr)
library(dplyr)
library(ggplot2)
library(printr)
library(fivethirtyeight)

# set up bibliography for citations
# if using knitcitations
#cleanbib()
#options("citation_format" = "pandoc")
```

# Preface {-}

This should be s short 2-3 paragraph summary of the book, what it is about and such.

## Why read this book {-}

This should cover the purpose of the book and what the read will gain after reading the book. 

Include who this book is for - having some previous experience with R is helpful, but a raw beginner could read these book - but it is assumed that the reader knows how to install software on their computer, connect to the Internet, find, create, copy and move files and folders on their computer. some previous experience working with document and presentation software like Word, google docs, open office, powerpoint, others xxxxxx...

Include things like:

* coursera course
* filling in the gaps
* seemingly disconnected applications brought together with rmarkdown glue

## Structure of the book {-}

A verbal summary of what is in the book, each capte or section, organization and workflow - does it have to be sequential or can the reader jump around as needed - have to reads versus optional reads...

## Software information and conventions {-}

Software assumptions, workflow and style conventions used in book. Maybe include stuff here on hints, warnings, and such.

## Acknowledgments {-}

People to thank:

* emory, cfde, tnt team 
* coursera
* chester ismay - fivethirtyeight package and feedback
* yihui xie - online help and guidance with bookdown
* developers of R, Rstudio, rmarkdown, bookdown, knitr, ...

## Prerequisites {-}

Placeholder for now - maybe come back and add details on getting started - what assumptions are made for getting setup to work thriugh the exercises in this book - to get the full experience...

See more in the "Getting Started" Chapter \@ref(getstarted).

***

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

## Colophon {-}

### R Packages Used in This Book {-}

This book will use the `R` programming language [@R-base] with the following `R` packages:

1. `bookdown` [@R-bookdown]
2. `rmarkdown` [@R-rmarkdown]
3. `knitr` [@R-knitr]
4. `dplyr` [@R-dplyr]
5. `ggplot2` [@R-ggplot2]
6. `printr` [@R-printr]
7. `fivethirtyeight` [@R-fivethirtyeight]

```{r include=FALSE}
# create a bib database for R packages
knitr::write_bib(c(.packages(), 
                   'bookdown', 'rmarkdown',
                   'knitr', 'dplyr',
                   'ggplot2', 'printr',
                   'fivethirtyeight'), 
                 'packages.bib')
```

Other external refs, book [@xie2015], and the FAD ref [@Miller_Epstein_Bishop_Keitner_1985].

### R Session Info as of `r Sys.time()` {-}

This book was compiled using the `R` packages `bookdown`, `rmarkdown`, and `knitr` running under the following `sessionInfo()`:

```{r session}
#Sys.time()
sessionInfo()
```

