--- 
title: "Reproducible Templates for Analysis and Dissemination - a practical introduction - DRAFT"
author: "Melinda K. Higgins"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [manual.bib, packages.bib]
biblio-style: apalike
link-citations: yes
lot: true
lof: true
description: "Reproducible Templates, Reproducible Research, R and RStudio, Git and Github, rmarkdown, knitr, blogdown, bookdown"
---

```{r pkgs1, include=FALSE}
# set up knitr chunk options

# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(message = FALSE)

# set up packages needed
library(bookdown)
library(rmarkdown)
library(knitr)
library(dplyr)
library(ggplot2)
library(printr)
library(fivethirtyeight)

# set up bibliography for citations
# if using knitcitations
#cleanbib()
#options("citation_format" = "pandoc")
```


# Preface {-}

\markboth{PREFACE}{PREFACE}

This book details tools and skills to improve your analyses by linking data, code and results dissemination (e.g., report, presentation, website, dashboard) into a seamless workflow. This book will help you create reusable workflow templates to improve your own efficiency. This information will also assist you with recreating a workflow that a previous coworker completed, revisiting a project you abandoned some time ago, or simply reproducing a document with a consistent format and process. Incomplete information about how the work was done, where the files are, and which is the most recent version can give rise to many complications. This book focuses on the proper end product creation process, allowing you and your colleagues to easily reproduce the components of your analyses. Throughout the exercises in this book, you will work with the R programming language, the RStudio IDE (interactive development interface) and the R Markdown package to help you build a portfolio of effective templates for reproducible analysis workflows.

## Why read this book {-}

While the reproducible research / reproducible analysis arena has been around for a decade or so, and is currently expanding to many industries and research areas, easy to read books with step-by-step instructions on setting up your own reproducible workflow are still hard to find. As described in the list of competitive books below, most of these current “R markdown”, “Reproducible Research”, and related books focus on the details associated with specific R package functions and options or do a fairly deep dive on the technical aspects of using and customizing R markdown. While some of them do provide example code for creating a “my first document”, none of them show how make use of a core set of data and analysis codes to produce multiple end products leveraging a consistent reproducible workflow infrastructure. In fact, I plan to use many of these books as references and recommended supplemental reading for readers who want to go more in-depth on any of the topics and related R packages. I plan to use the same dataset and R analysis codes in every chapter for consistency, so the reader can focus on the wide range of possibilities for formatting and disseminating their results to a multitude of audiences across different platforms (hardcopy, digital, and web-based).

This book will achieve it’s goals by providing step-by-step instructions and accompanying code to walk the reader through creating different types of end products for disseminating and communicating their results to a wide-array of audiences. Separate chapters will focus on creating specific end products such as:

* creating traditional report document formats (such as PDF, DOC, and OTF) and even HTML static webpage formats;
* creating presentation slide formats (such as Beamer, ioslides, slidy, and PowerPoint);
* presenting results online through websites and dashboards;
* creating book type presentations in either hard copy formats (PDF) or electronic book formats

By the end of each chapter, the reader will have created an end-to-end workflow template for that chapter’s format (e.g. document, slides, website, dashboard, book) that can be easily reused and customized for their specific data, analyses and formatting. For example, a single analysis could be disseminated simultaneously in multiple ways such through a quarterly report, blog post, dashboard and website with a project or company logo.

This book will also include an accompanying Github repository with all of the data, code, templates and supporting files for all of the exercises in the book. This will include an R package that the reader can install for ready access to the datasets, code, and R markdown templates used in the book. These will enable the reader to be immediately productive using what they learned in the book.

... other thoughts ...

Include who this book is for - having some previous experience with R is helpful, but a raw beginner could read these book - but it is assumed that the reader knows how to install software on their computer, connect to the Internet, find, create, copy and move files and folders on their computer. some previous experience working with document and presentation software like Word, google docs, open office, powerpoint, others xxxxxx...

Include things like:

* coursera course
* filling in the gaps
* seemingly disconnected applications brought together with rmarkdown glue

### Coursera Course {-}

This book is <font color="red">based on</font> the Coursera Course "Reproducible Templates for Analysis and Dissemination", [https://www.coursera.org/learn/reproducible-templates-analysis](https://www.coursera.org/learn/reproducible-templates-analysis)

**Coursera Course Description:** _"This course will assist you with recreating work that a previous coworker completed, revisiting a project you abandoned some time ago, or simply reproducing a document with a consistent format and workflow. Incomplete information about how the work was done, where the files are, and which is the most recent version can give rise to many complications. This course  focuses on the proper documentation creation process, allowing you and your colleagues to easily reproduce the components of your workflow. Throughout this course, you'll receive helpful demonstrations of RStudio and the R Markdown language and engage in active learning opportunities to help you build a professional online portfolio."_

The Course consists of 5 Modules:

1. Introduction to Reproducible Research and Dynamic Documentation
    * This module provides an introduction to the concepts surrounding reproducibility and the Open Science movement, RStudio and GitHub, and foundational cases and authors in the field.
    * 11 videos, 6 readings, 1 practice quiz
    
2. R Markdown: Syntax, Document, and Presentation Formats
    * This module explores the R Markdown syntax to format and customize the layout of presentations or reports and will also look at inserting and creating objects such as tables, images, or video within documents.
    * 8 videos, 11 readings, 1 practice quiz
    
3. R Markdown Templates: Processing and Customizing
    * This module goes further with R Markdown to help turn documents, reports, and presentations into templates for easier automation, reproducibility, and customization.
    * 9 videos, 6 readings, 1 practice quiz
    
4. Leveraging Custom Templates from Leading Scientific Journals
    * This module delves into custom templates available for websites, books, and scientific publishers, such as Elsevier and the IEEE, with the chance to create your first R Package.
    * 6 videos, 3 readings, 1 practice quiz
    
5. Working in Teams and Disseminating Templates and Reports
    * This module focuses on helpful tips for sharing and using the templates you create, as well as methods for organizing content. We'll also look at a few web-publishing services.
    * 6 videos, 2 readings, 1 practice quiz

## Structure of the book {-}

A verbal summary of what is in the book, each chapter or section, organization and workflow - does it have to be sequential or can the reader jump around as needed - have to reads versus optional reads...

... will be added once final structure of book is completed ...

## Software information and conventions {-}

Software assumptions, workflow and style conventions used in book. Maybe include stuff here on hints, warnings, and such.

This will include layout of consistency, standard structure and workflow practices used for each chapter.

## Acknowledgments {-}

People to thank:

* emory, cfde, tnt team 
* coursera
* chester ismay - fivethirtyeight package and feedback
* yihui xie - online help and guidance with bookdown
* developers of R, Rstudio, rmarkdown, bookdown, knitr, ...
* other who may/will help in reading, feedback, revisions, etc...

## Prerequisites {-}

Placeholder for now - maybe come back and add details on getting started - what assumptions are made for getting setup to work thriugh the exercises in this book - to get the full experience...

See more in the "Getting Started" Chapter \@ref(getstarted).

***

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

## Colophon {-}

### R Packages Used in This Book {-}

This book will use the `R` programming language [@R-base] with the following `R` packages:

1. `bookdown` [@R-bookdown]
2. `rmarkdown` [@R-rmarkdown]
3. `knitr` [@R-knitr]
4. `dplyr` [@R-dplyr]
5. `ggplot2` [@R-ggplot2]
6. `printr` [@R-printr]
7. `fivethirtyeight` [@R-fivethirtyeight]

```{r include=FALSE}
# create a bib database for R packages
knitr::write_bib(c(.packages(), 
                   'bookdown', 'rmarkdown',
                   'knitr', 'dplyr',
                   'ggplot2', 'printr',
                   'fivethirtyeight'), 
                 'packages.bib')
```

Other external refs, book [@xie2015], and the FAD ref [@Miller_Epstein_Bishop_Keitner_1985].

### R Session Info as of `r Sys.time()` {-}

This book was compiled using the `R` packages `bookdown`, `rmarkdown`, and `knitr` running under the following `sessionInfo()`:

```{r session}
#Sys.time()
sessionInfo()
```

