--- 
title: "Reproducible Templates _(Book in Development)_"
author: "Melinda K. Higgins"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [manual.bib, packages.bib]
biblio-style: apalike
link-citations: yes
lot: true
lof: true
description: "Reproducible Templates, Reproducible Research, R and RStudio, Git and Github, rmarkdown, knitr, blogdown, bookdown"
---

```{r pkgs1, include=FALSE}
# set up knitr chunk options

# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(message = FALSE)

# set up packages needed
library(bookdown)
library(rmarkdown)
library(knitr)
library(dplyr)
library(ggplot2)
library(printr)
library(fivethirtyeight)

# set up bibliography for citations
# if using knitcitations
#cleanbib()
#options("citation_format" = "pandoc")
```


# Preface {-}

\markboth{PREFACE}{PREFACE}

This should be s short 2-3 paragraph summary of the book, what it is about and such.

## Why read this book {-}

This should cover the purpose of the book and what the read will gain after reading the book. 

Include who this book is for - having some previous experience with R is helpful, but a raw beginner could read these book - but it is assumed that the reader knows how to install software on their computer, connect to the Internet, find, create, copy and move files and folders on their computer. some previous experience working with document and presentation software like Word, google docs, open office, powerpoint, others xxxxxx...

Include things like:

* coursera course
* filling in the gaps
* seemingly disconnected applications brought together with rmarkdown glue

### Coursera Course {-}

This book is <font color="red">based on</font> the Coursera Course "Reproducible Templates for Analysis and Dissemination", [https://www.coursera.org/learn/reproducible-templates-analysis](https://www.coursera.org/learn/reproducible-templates-analysis)

**Coursera Course Description:** _"This course will assist you with recreating work that a previous coworker completed, revisiting a project you abandoned some time ago, or simply reproducing a document with a consistent format and workflow. Incomplete information about how the work was done, where the files are, and which is the most recent version can give rise to many complications. This course  focuses on the proper documentation creation process, allowing you and your colleagues to easily reproduce the components of your workflow. Throughout this course, you'll receive helpful demonstrations of RStudio and the R Markdown language and engage in active learning opportunities to help you build a professional online portfolio."_

The Course consists of 5 Modules:

1. Introduction to Reproducible Research and Dynamic Documentation
    * This module provides an introduction to the concepts surrounding reproducibility and the Open Science movement, RStudio and GitHub, and foundational cases and authors in the field.
    * 11 videos, 6 readings, 1 practice quiz
    
2. R Markdown: Syntax, Document, and Presentation Formats
    * This module explores the R Markdown syntax to format and customize the layout of presentations or reports and will also look at inserting and creating objects such as tables, images, or video within documents.
    * 8 videos, 11 readings, 1 practice quiz
    
3. R Markdown Templates: Processing and Customizing
    * This module goes further with R Markdown to help turn documents, reports, and presentations into templates for easier automation, reproducibility, and customization.
    * 9 videos, 6 readings, 1 practice quiz
    
4. Leveraging Custom Templates from Leading Scientific Journals
    * This module delves into custom templates available for websites, books, and scientific publishers, such as Elsevier and the IEEE, with the chance to create your first R Package.
    * 6 videos, 3 readings, 1 practice quiz
    
5. Working in Teams and Disseminating Templates and Reports
    * This module focuses on helpful tips for sharing and using the templates you create, as well as methods for organizing content. We'll also look at a few web-publishing services.
    * 6 videos, 2 readings, 1 practice quiz

## Structure of the book {-}

A verbal summary of what is in the book, each capte or section, organization and workflow - does it have to be sequential or can the reader jump around as needed - have to reads versus optional reads...

## Software information and conventions {-}

Software assumptions, workflow and style conventions used in book. Maybe include stuff here on hints, warnings, and such.

## Acknowledgments {-}

People to thank:

* emory, cfde, tnt team 
* coursera
* chester ismay - fivethirtyeight package and feedback
* yihui xie - online help and guidance with bookdown
* developers of R, Rstudio, rmarkdown, bookdown, knitr, ...

## Prerequisites {-}

Placeholder for now - maybe come back and add details on getting started - what assumptions are made for getting setup to work thriugh the exercises in this book - to get the full experience...

See more in the "Getting Started" Chapter \@ref(getstarted).

***

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

## Colophon {-}

### R Packages Used in This Book {-}

This book will use the `R` programming language [@R-base] with the following `R` packages:

1. `bookdown` [@R-bookdown]
2. `rmarkdown` [@R-rmarkdown]
3. `knitr` [@R-knitr]
4. `dplyr` [@R-dplyr]
5. `ggplot2` [@R-ggplot2]
6. `printr` [@R-printr]
7. `fivethirtyeight` [@R-fivethirtyeight]

```{r include=FALSE}
# create a bib database for R packages
knitr::write_bib(c(.packages(), 
                   'bookdown', 'rmarkdown',
                   'knitr', 'dplyr',
                   'ggplot2', 'printr',
                   'fivethirtyeight'), 
                 'packages.bib')
```

Other external refs, book [@xie2015], and the FAD ref [@Miller_Epstein_Bishop_Keitner_1985].

### R Session Info as of `r Sys.time()` {-}

This book was compiled using the `R` packages `bookdown`, `rmarkdown`, and `knitr` running under the following `sessionInfo()`:

```{r session}
#Sys.time()
sessionInfo()
```

