--- 
title: "DRAFT Book Reproducible Templates"
author: "Melinda K. Higgins"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [manual.bib, packages.bib]
biblio-style: apalike
link-citations: yes
lot: true
lof: true
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

```{r pkgs1, include=FALSE}
# set up knitr chunk options

# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(message = FALSE)

# set up packages needed
library(bookdown)
library(rmarkdown)
library(knitr)
library(dplyr)
library(ggplot2)
library(printr)
library(fivethirtyeight)

# set up bibliography for citations
#cleanbib()
#options("citation_format" = "pandoc")

```


# Preface {-}

aaaaaaaaaaaa

## Why read this book {-}

aaaaaaaaaaaaa

## Structure of the book {-}

aaaaaaaaaaaaaaaa

## Software information and conventions {-}

aaaaaaaaaaaaaaaa

## Acknowledgments {-}

aaaaaaaaaaaaaaa

## Prerequisites {-}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need to install XeLaTeX.

## Colophon {-}

### R Packages Used in This Book {-}

This book will use the `R` programming language [@R-base] with the following `R` packages:

1. `bookdown` [@R-bookdown]
2. `rmarkdown` [@R-rmarkdown]
3. `knitr` [@R-knitr]
4. `dplyr` [@R-dplyr]
5. `ggplot2` [@R-ggplot2]
6. `printr` [@R-printr]
7. `fivethirtyeight` [@R-fivethirtyeight]

```{r include=FALSE}
# create a bib database for R packages
knitr::write_bib(c(.packages(), 
                   'bookdown', 'rmarkdown',
                   'knitr', 'dplyr',
                   'ggplot2', 'printr',
                   'fivethirtyeight'), 
                 'packages.bib')
```

Other external refs, book [@xie2015], and the FAD ref [@Miller_Epstein_Bishop_Keitner_1985].

### R Session Info as of `r Sys.time()` {-}

This book was compiled using the `R` packages `bookdown`, `rmarkdown`, and `knitr` running under the following `sessionInfo()`:

```{r session}
#Sys.time()
sessionInfo()
```

